Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
chore: same formulas

In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
\begin{algorithm}
  \caption{Neighboring-Based Deep Q-Learning}
  \label{alg:neighbor_dqn}
  \ForEach{agent $i \in N$}{
      Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
      Initialize replay buffer $\mathcal{B}^i$
  }
  \For{episode = 1 to M}{
      \ForEach{agent $i \in N$}{
          Initialize initial observation $o_0^i$
      }
      \For{t = 0 to T}{
          \ForEach{agent $i \in N$}{
              Select action $a_t^i$ based on $\epsilon$-greedy policy using $Q^i(o_t^i, a^i; \theta^i)$\\
              Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{B}^i$\\
              Sample a mini-batch from $\mathcal{B}^i$\\
              Calculate target values using chosen neighboring strategy (see below)\\
              Update $\theta^i$ by minimizing the TD error\\
              Every C steps, update target network $\theta^{i-} \leftarrow \theta^i$\\
              \textbf{
              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
          }
      }
  }
\end{algorithm}

>>>>

In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
\begin{algorithm}
  \caption{Neighboring-Based Deep Q-Learning}
  \label{alg:neighbor_dqn}
  \ForEach{agent $i \in N$}{
      Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
      Initialize replay buffer $\mathcal{D}^i$
  }
  \For{episode = 1 to M}{
      \ForEach{agent $i \in N$}{
          Initialize initial observation $o_0^i$
      }
      \For{t = 0 to T}{
          \ForEach{agent $i \in N$}{
              Select action $a_t^i$ based on $\epsilon$-greedy policy using $Q^i(o_t^i, a^i; \theta^i)$\\
              Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{D}^i$\\
              Sample a mini-batch from $\mathcal{D}^i$\\
              Calculate target values using chosen neighboring strategy (see below)\\
              Update $\theta^i$ by minimizing the TD error\\
              Every C steps, update target network $\theta^{i-} \leftarrow \theta^i$\\
              \textbf{
              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
          }
      }
  }
\end{algorithm}
